### 2022-01-19 src-latex/parts/50-xp-setup.tex
adds spacy & hf libs versions

\subsubsection{Spacy}
We use the French pipeline \textit{fr\_core\_news\_lg} provided by SpaCy\mcite{spacy}, already trained for NER on the deep-sequoia and wikiner-fr corpora.
The default NER labels known to the pipeline are PER, ORG, MISC and LOC.
In experiment 1 the base model is fine-tuned on every of the 8 training sets using the same training parameters.
Early stopping is activated with a patience value of 1600 training steps without improvement of the f1 score.

@@

\subsubsection{Huggingface CamemBERT}
Experiments 1 and 2 rely on the implementation of transformers provided by the software library Huggingface.
Our baseline CmBERT model is CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
Its NER head is a linear model with a Softmax function.
CmBERT and CmBERT+ptrn are always fine-tuned using the same parameters, with at most 5000 training steps and an early stopping condition set to 3 evaluations in experiment 1 (5 in experiment 2) without improvement of the f1 score. Evaluations are run every 100 steps.

>>>>

\subsubsection{Spacy}
We use the French pipeline \textit{fr\_core\_news\_lg} provided by SpaCy v.3.2.1\mcite{spacy}, already trained for NER on the deep-sequoia and wikiner-fr corpora.
The default NER labels known to the pipeline are PER, ORG, MISC and LOC.
In experiment 1 the base model is fine-tuned on every of the 8 training sets using the same training parameters.
Early stopping is activated with a patience value of 1600 training steps without improvement of the f1 score.

@@

\subsubsection{Huggingface CamemBERT}
Experiments 1 and 2 rely on the implementation of transformers provided by the software library Huggingface (transformers v.4.15.0, datasets v.1.17.0).
Our baseline CmBERT model is CamemBERT model published on the Hugging Face repository \footnote{\url{https://huggingface.co/Jean-Baptiste/camembert-ner}} and already trained for NER on wikiner-fr.
Its NER head is a linear model with a Softmax function.
CmBERT and CmBERT+ptrn are always fine-tuned using the same parameters, with at most 5000 training steps and an early stopping condition set to 3 evaluations in experiment 1 (5 in experiment 2) without improvement of the f1 score. Evaluations are performed every 100 steps.
